---
title: "R Notebook"
output: html_notebook
---

```{r}
library(plotly)
library(tidyverse)
library(dplyr)
library(thematic)
library(RColorBrewer)
library(ggiraph)
library(ggplot2)
library(reshape2)
```


```{r}
travel
str(travel)
```
```


```{r}
ck<-travel%>%
  plot_ly(x = ~Duration, y = ~Commision..in.value., type = 'scatter', mode = 'markers')%>%
  add_annotations(
    text = ~unique(Duration),
    xref="Duration",
    yref="Commision"
  )
  
ck
```

```{r}
plt_hst <- travel%>%
  ggplot(aes(x=Commision..in.value.)) + geom_histogram(binwidth=2,colour="black")+
  facet_grid(Gender ~ Agency.Type, scales="free_y")+
  labs(
     y="",
     x="Commision"
  )+
  theme_minimal()

plot2<-ggplotly(plt_hst)

plot2
```

```{r}
plot2 <- function(d) {
  plot_ly(d, x = ~Duration) %>%
    add_annotations(
      ~unique(Gender), x = 0.5, y = 1, 
      xref = "paper", yref = "paper", showarrow = FALSE
    )
}

travel %>%
  split(.$Gender) %>%
  lapply(plot2) %>% 
  subplot(nrows = 2, shareX = TRUE, titleX = FALSE) %>%
  hide_legend()
```


